Notes on 10d Super Yang-Mills

### 2019-03-01 10d_SYM_Notes.tex
Continuing 10d SUSY action description

\subsection{On-Shell Supersymmetry Action}
We can define an action of the 10d $\mc N=1$ supersymmetry algebra on the complex of BRST fields in this minimal super Yang-Mills theory.  The Poincar\'e action is clear, and the action of the supersymmetry $Q$ is generated -- in the usual Physics notation -- by the transformation \cite{BrinkSchwarzScherk}
\begin{align*}
\delta_Q A &= \Gamma(Q,\lambda) \\
\delta_Q \lambda &= \sd F_A Q,
\end{align*}
where the notation $\sd F_A$ stands for the iterated Clifford multiplication $\sd F_A = F_{ij} \gamma^i \gamma^j$.  To check that this defines a supersymmetry action we need to check it's compatible with the brackets in the supersymmetry algebra.  So, we calculate
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] A &= (\Gamma(Q_2,\sd F_A Q_1) - \Gamma(Q_1,\sd F_A Q_2)) \\
&=  F_{ij}(Q_2 \gamma^k \gamma^i \gamma^j Q_1 - Q_1 \gamma^k \gamma^i \gamma^j Q_2)\\
&=  F_{ij}(Q_2 \gamma^k \gamma^i \gamma^j Q_1 - Q_2 \gamma^j \gamma^i \gamma^k Q_1)\\
&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 - Q_2 \gamma^j \gamma^k \gamma^i Q_1)\\
&=  F_{ij}\delta^{kj}(Q_2 \gamma^i Q_1) \\
&= \delta_{[Q_1, Q_2]} A,
\end{align*}
where on the third line we used the fact that the pairing $\Gamma(-,-)$ is symmetric, i.e. $\lambda_1 \gamma^i \lambda_2 = \lambda_2 \gamma^i \lambda_1$, three times, and on the fourth and fifth lines we used the Clifford relations.  Similarly we can calculate
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] \lambda &= (\sd F_{\Gamma(Q_2, \lambda)} Q_1 - \sd F_{\Gamma(Q_1,\lambda)} Q_2) \\
&= 
\end{align*}

>>>>

\subsection{On-Shell Supersymmetry Action}
We can define an action of the 10d $\mc N=1$ supersymmetry algebra on the complex of BRST fields in this minimal super Yang-Mills theory.  The Poincar\'e action is clear, and the action of the supersymmetry $Q$ is generated -- in the usual Physics notation -- by the transformation \cite{BrinkSchwarzScherk}
\begin{align*}
\delta_Q A &= \Gamma(Q,\lambda) \\
\delta_Q \lambda &= \sd F_A Q,
\end{align*}
where the notation $\sd F_A$ stands for the iterated Clifford multiplication $\sd F_A = F_{ij} \gamma^i \gamma^j$.  To check that this defines a supersymmetry action we need to check it's compatible with the brackets in the supersymmetry algebra.  So, we calculate
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] A &= (\Gamma(Q_2,\sd F_A Q_1) - \Gamma(Q_1,\sd F_A Q_2)) \\
&=  F_{ij}(Q_2 \gamma^k \gamma^i \gamma^j Q_1 - Q_1 \gamma^k \gamma^i \gamma^j Q_2)\\
&=  F_{ij}(Q_2 \gamma^k \gamma^i \gamma^j Q_1 - Q_2 \gamma^j \gamma^i \gamma^k Q_1)\\
&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 - Q_2 \gamma^j \gamma^k \gamma^i Q_1)\\
&=  F_{ij}\delta^{kj}(Q_2 \gamma^i Q_1) \\
&= \delta_{[Q_1, Q_2]} A,
\end{align*}
where on the third line we used the fact that the pairing $\Gamma(-,-)$ is symmetric -- i.e. that $\lambda_1 \gamma^i \lambda_2 = \lambda_2 \gamma^i \lambda_1$ -- three times, and on the fourth and fifth lines we used the Clifford relations.  Similarly we can calculate
\begin{align*}
[\delta_{Q_1}, \delta_{Q_2}] \lambda &= (\sd F_{\Gamma(Q_2, \lambda)} Q_1 - \sd F_{\Gamma(Q_1,\lambda)} Q_2) \\
&= (Q_2 \gamma_j \dd_i \lambda + [Q_2\gamma_i \lambda, Q_2 \gamma_j \lambda]) (\gamma^i \gamma^j Q_1) - (1 \leftrightarrow 2) \\
&= 
\end{align*}

\begin{remark}
I'm part way through trying to do these calculations myself, but for reference I found these calculations in the master's thesis \cite{Guillen} we've discussed before.  For instance for the commutator of two supersymmetries acting on a spinor see equation 2.1.13.
\end{remark}
